Comparing to lognormal, Poisson, exponential

### 2021-03-09 analysis/rev_prototyping/ct_mcdb.Rmd
methods

ggplot(all_di, aes(sim_pos_from_best, real_po)) +
  geom_point() +
  geom_line(aes(sim_pos_from_best, sim_pos_from_best))

>>>>

ggplot(all_di, aes(sim_pos_from_best, real_po, color = real_po_percentile_excl > 95)) +
  geom_point() +
  geom_line(aes(sim_pos_from_best, sim_pos_from_best)) +
  theme(legend.position = "top")
